\documentclass[aspectratio=169]{beamer}
\usetheme{metropolis}
\hypersetup{colorlinks=true, linkcolor=cyan, urlcolor=cyan, citecolor=cyan}

\title{MGMT 638}
\subtitle{Session 7}
\author{Kerry Back}
\institute{}
\date{Fall 2025}

\begin{document}

\maketitle

\begin{frame}{Agenda}
\begin{enumerate}
\item Algos, HFTs, and quants
\item Alphas and portfolio improvement 
\item data2\_nov2025.xlsx
\item Traditional stock analysis (valuation by multiples)
\end{enumerate}
\end{frame}


\begin{frame}{Algos, HFTs, and Quants}
\begin{itemize}
\item Algorithmic trading: using an algorithm to optimally execute a large order over time 
\item High frequency trading: submitting and cancelling orders to earn bid-ask spreads or to hit bids and asks that are slightly mispriced
\item Quantitative investing: longer-horizon investing based on quantitative signals
\item \href{https://mgmt638.kerryback.com/videos/Algos_HFTs_Quants_Explained.mp4}{Algos, HFTs, and Quants Explained video}
\item \href{https://mgmt638.kerryback.com/videos/Quant_Investing_Revolution.mp4}{Quant Investing Revolution video}
\end{itemize}
\end{frame}



\begin{frame}{New Dataset}

\begin{itemize}
\item Download \href{https://www.dropbox.com/scl/fi/yggnxyx32zjk1oxhzkidc/data2\_nov2025.xlsx?rlkey=sx8nzw91easc7e5fkjn1bpzn3&dl=1}{data2\_nov2025.xlsx}
\item Ask Claude to describe the data and to list all columns.
\end{itemize}
\end{frame}

\begin{frame}{Traditional Stock Analysis}
\begin{itemize}
\item Let's pick a stock to analyze.
\item Ask Claude to use the data2\_nov2025.xlsx data to find stocks in the same industry with similar marketcaps and to list their PE and PB ratios, ROE, and 5-year revenue growth.
\item Does the company we're analyzing look undervalued, overvalued, or correctly valued?
\item Try to understand the company's valuation using other data from data2\_nov2025.xlsx.  And ask Claude to get other data as needed from the Rice database.
\end{itemize}
\end{frame}


\begin{frame}{Research Report}
\begin{itemize}
\item Ask Claude to do online research to find any information relevant to the company's valuation.
\item Ask Claude to create a Word doc containing an analysis of the company based on the peer data, any other data gathered, and the online research.
\item Is there other information we would want to look at?
\end{itemize}
\end{frame}

\end{document}
