\documentclass[aspectratio=169]{beamer}
\usetheme{metropolis}
\hypersetup{colorlinks=true, linkcolor=cyan, urlcolor=cyan, citecolor=cyan}

\title{MGMT 638}
\subtitle{Session 4}
\author{Kerry Back}
\institute{}
\date{Fall 2025}

\begin{document}

\maketitle

\begin{frame}{Agenda}
    \begin{itemize}
    \item Data
    \item Using sorts to evaluate characteristics
    \item Building a streamlit stock recommender app
    \item Profitability characteristic 
    \item Sorting on multiple characteristics
    \end{itemize}
\end{frame}

\begin{frame}{Data}
\begin{itemize}
\item Download \href{https://www.dropbox.com/scl/fi/5l4woqke5cn6tuu8wwdta/data1.parquet?rlkey=j917tet66yfsxniqwi5ld8u7c&dl=1}{data1.parquet}
\item Monthly data for all stocks in database for Feb, 2011 through Oct, 2025
\item Return, momentum, market cap, equity, assets, gross profit, operating profit, net income (netinccmn), asset growth rate (agr)
\item Tell Claude to read the data and add the following variables:
\begin{itemize}
\item bm (book-to-market) $=$ equity / marketcap
\item gpa $=$ gross profits / assets 
\item roe $=$ netinccmn / equity
\item opr $=$ operating profit / equity
\item lagret $=$ return shifted one month forward after grouping by ticker
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Sorting}

\begin{itemize}
\item Pick a characteristic: size (marketcap), value (book-to-market), momentum, lagret, agr, opr, gpa, or roe
\item Tell Claude;
\begin{itemize}
\item Sort by the characteristic each month into deciles.
\item Then calculate the average return of each decile each month.
\end{itemize} 
\item We now have returns of 10 portfolios that could have been constructed in real time.
\item We're selecting stocks at the beginning of each month, investing the same amount in each stock, and holding for a month.
\item Which of the 10 portfolios did better?  What criteria will you use to decide?
\end{itemize}
\end{frame}

\begin{frame}{Streamlit}
    \begin{itemize}
    \item Your 1st assignment is due Sunday night.  It is to build a Streamlit stock recommender app.
    \item Trial run.  Tell Claude:
    \begin{itemize}
    \item Sort stocks into quartiles based on some stock characteristic for November, 2025.
    \item Label the best quartile as `Buy', the worst quartile as `Sell', and the middle half as `Hold.'
    \item Build a Streamlit app that prompts the user for a ticker and then displays the recommendation or `Not Classified' if the ticker is not in the data set.
\item Run the streamlit app.
\end{itemize} 
\end{itemize}
\end{frame}

\begin{frame}{Profitability}
\begin{itemize}
\item \href{https://mgmt638.kerryback.com/pdfs/Novy-Marx_Medhat_2025.pdf}{PDF: Novy-Marx and Medhat, 2025}
\item \href{https://mgmt638.kerryback.com/videos/Novy-Marx_Medhat_2025.mp4}{Video: Novy-Marx and Medhat, 2025}
\item \href{https://notebooklm.google.com/notebook/5a303502-e158-49bb-bd81-a20c35a00b8d}{NotebookLM}
\end{itemize}
\end{frame}

\begin{frame}{Sorting on Multiple characteristics}
    \begin{itemize}
    \item We can group stocks based on multiple characteristics.
    \item If we use a lot of characteristics and a lot of groups, some groups may be unpopulated or sparsely populated.
    \item characteristics usually only work in diversified portfolios, because characteristics are weak predictors.
    \item Examples that should be OK:
    \begin{itemize}
    \item Two characteristics and quintiles $\Rightarrow$ 25 portfolios
    \item Three characteristics and terciles $\Rightarrow$ 27 portfolios
    \end{itemize}
    \item Try momentum and book-to-market.  Tell Claude to sort into quintiles on each characteristic each month and to compute the average return each month in each of the 25 groups.  What is the best group?
    \end{itemize}
\end{frame}
\end{document}
